%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{tikz}
\usepackage{array}

\newcommand{\fc}{\tikz\draw[black,fill=black] (0,0) circle (.5ex);}%
\newcommand{\ec}{\tikz\draw[black,fill=white] (0,0) circle (.5ex);}%

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Michal }{Parusinski}{Lead Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
    {\def\arraystretch{0.3}%
    \begin{tabular}{l}
    2 rue du général Streicher,
    67120 Molsheim, France \\
    +33 (0)6 52 22 90 13 \\
    \href{mailto:michal@parusinski.me}{michal@parusinski.me} \\
    \href{https://michal.parusinski.me}{michal.parusinski.me} \\
    \end{tabular}%
    }
\section{languages}
    {\def\arraystretch{0.3}%
    \begin{tabular}{m{5em} m{5em}}
        \emph{french} & \fc\fc\fc\fc\fc \\
        \emph{english} & \fc\fc\fc\fc\fc \\
        \emph{polish} & \fc\fc\fc\fc\ec \\
        \emph{german} & \fc\fc\ec\ec\ec \\
    \end{tabular}%
    }
\section{programming}
    {\def\arraystretch{0.3}%
    \begin{tabular}{m{5em} m{5em}}
        \emph{C / C++} & \fc\fc\fc\fc\ec \\
        \emph{Java} & \fc\fc\fc\ec\ec \\
        \emph{Python} & \fc\fc\fc\fc\ec \\
        \emph{Haskell} & \fc\fc\fc\fc\ec \\
        \emph{Javascript} & \fc\fc\fc\ec\ec \\
        \emph{PHP} & \fc\fc\ec\ec\ec \\
    \end{tabular}%
    }
\section{IT skills}
    {\def\arraystretch{0.3}%
    \begin{tabular}{l}
        \emph{Unix/Linux} \\
        \emph{Agile methods} \\
        \emph{Object oriented} \\
        \emph{Machine learning} \\
        \emph{Distributed computing} \\
        \emph{Cloud infrastructure} \\
        \emph{Cybersecurity} \\
    \end{tabular}%
    }
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------ 
\entry
{2008--2012}
{master {\normalfont Msci. Mathematics \& Computer Science}}
{Imperial College London}
{First class honours}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{professional experiences}

\subsection{full time}

\begin{entrylist}

%------------------------------------------------


\entry
{2018--2022}
{ICube-SERTIT}
{Illkirch Graffenstaden, France}
{\emph{Software engineer}
\medbreak
Automating extraction of geographical information from satellite imagery
using deep learning et AI model generalization through GAN data augmentation.
\smallbreak
Development of a Software as a Service platform for end-to-end burnt areas
and floods mapping pipeline.
\smallbreak
Web mapping platform for SERTIT's mapping products
}

\entry
{2015--2018}
{Amadeus}
{Sophia-Antipolis, France}
{\emph{Software engineer and technical leader}
\medbreak
I worked on reservations systems for Car Rental, Insurance and Cruise; both
on ”backend” and ”frontend” side.
\smallbreak
Also worked on reengineering of the reservation system operating on IBM
mainframe to a distributed modern architecture running on Linux servers
(TPF Deco).
\bigbreak %
}

\entry
{2013--2015}
{IBM}
{Hursley, Royaume-Uni}
{\emph{Software developer}
\medbreak
QA tester for SPSS Modeler and SPSS Entity Analytics: Test creation and
maintenance of multiple test systems (Unix and Windows).
\smallbreak
Software engineer for SPSS Modeler: Development of functionality such as
support for the PowerPC architecture and integration of the software with
the IBM Bluemix cloud platform.
\bigbreak %
}

\entry
{2012--2013}
{Université Catholique de Louvain}
{Louvain-la-Neuve, Belgique}
{\emph{Research Assistant}
\medbreak
Project on Physically Unclonable Functions: I have used the logistic regression
to attack a PUF built on power consumption.
}
%------------------------------------------------

\end{entrylist}

\newpage

\subsection{internships}

\begin{entrylist}

\entry
{Summer 2011}
{Siemens}
    {Princeton, United-States}
{\emph{Summer intern}
\medbreak
Contribution to a medical imaging platform built for heart simulations and
heart surgery assistance. Coding was done in C++, OpenGL and OpenMP.
\bigbreak
}

\entry
{2011--2012}
{Imperial College London}
{London, Royaume-Uni}
{\emph{Undergraduate Teaching Assistant}
\medbreak
    Participation to the teaching of 1\textsuperscript{st} year formal logic lecture at Imperial College.
\bigbreak
}

\entry
{Summer 2010}
{Imperial College London}
{London, Royaume-Uni}
    {\emph{Research Intern (UROP)}
	\medbreak
    Contribution to a ocean simulation platform within the AMCG (Applied Modeling \& Computation Group) research group: Worked on data model adaptation for finite element method.
	\bigbreak
}

\entry
{Summer 2009}
{Personal Audio Ltd.}
{Sydney, Australie}
    {\emph{Software engineer}
	\medbreak
    Worked in a start-up focused on game experience enhancement. Created
an interface in QT.
	\bigbreak
}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{rewards}

\begin{entrylist}

%------------------------------------------------

\entry
{2008 \& 2011}
{Gloucester Research Prize}
{Imperial College London}
{Distinction for academic excellence}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional :} machine learning, data science, mathematics and
statistics, servers, UNIX
\medbreak
\textbf{personal :} martial arts, game of go, board games

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\textbf{scientific publication:} Coauthor of the scientific publication on physically unclonable functions
\href{https://perso.uclouvain.be/fstandae/PUBLIS/134.pd}{https://perso.uclouvain.be/fstandae/PUBLIS/134.pd}
\medbreak
\textbf{patent:} Coauthor of U.S. Patent
\href{http://patft.uspto.gov/netacgi/nph-Parser?Sect2=PTO1&Sect2=HITOFF&p=1&u=/netahtml/PTO/search-bool.html&r=1&f=G&l=50&d=PALL&RefSrch=yes&Query=PN/9582263}{9,582,263}
on wearable technologies

%----------------------------------------------------------------------------------------

\end{document}
